%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\begin{comment}
\cventry
{Software Engineer Intern}
{Microsoft}
{Redmond, Washington}
{Jun. 2018 - Sep. 2018}
{
\begin{cvitems}
\item {Will develop on the frameworks team}
\end{cvitems}
}
\end{comment}

\cventry
	{Software Engineer Intern}
	{Microsoft}
	{Redmond, Washington}
	{Jun. 2018 - Sep. 2018}
{								
	\begin{cvitems} 
                \item {Developed and shipped the Share Location feature which uses Apple's MapKit and Bing Maps API to send a geo-location message}
                \item {Developed and shipped the Audio Message feature which replaces the send button on our iOS client}
                \item {Created the backend services which uses Skype's Chat services and AMS to store raw audio data and map data securely}
                \item {Designed and developed a parser and inline renderer for both the Audio Message feature and the Share Location feature}
		\item {Integrated with many APIs and SDKs including \textbf{Google}, \textbf{Bing}, \textbf{Apple}, \textbf{Skype}, etc.}
                \item {Both features streamlined the messaging pipeline with improvements in performance by reducing the number of API calls}
		\item {\textbf{Both} features will officially ship to the \textbf{Apple App Store} soon}
	\end{cvitems}
}

\cventry
{Software Engineer Intern}
{Oracle}
{Redwood Shores, California}
{Sep. 2017 - Oct. 2017}
{
\begin{cvitems}
\item {Designed new functionality with pre-existing infrastructure to reduce redundancies in the backend}
\item {Evaluated previous system for \textbf{iOS} and \textbf{Android} applications to architect a plan to integrate a new workflow}
\end{cvitems}
}

\cventry
{Software Engineer Intern} % Job title
{Sentient Energy} % Organization
{Santa Clara, California} % Location
{Jun. 2017 - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a framework to automate validation of REST API for nightly builds saving \textbf{4 hours per method}}
\item {Utilized \textbf{machine learning via TensorFlow} to automate classification of new methods creating a scalable environment}
\item {Developed modules to parse information necessary to automate creation of the REST API scchema}
\item {Populate databases necessary for executing test cases by inducting from training data}
\item {Validates back end by verifying dependent databases after a successful API call eliminating manual validation}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineer Intern} % Job title
{Microcon} % Organization
{San Luis Obispo, California} % Location
{Sep. 2016 - Jun. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed the frontend of the Employee Portal using HTML5, and JavaScript}
\item {Developed the backend of the Employee Portal using C\# and Microsoft SQL Server}
\item {Integrated backend with previous database infrastructure to handle scalability by not saving redundant data}
\item {Created scripts for shipment processes during upgrades and releases}
\end{cvitems}
}

\cvsection{Projects}
%------ CV Entires


\cventry
{Back End Engineer} % Job title
{Facial Recognition Authentication for Clover Devices} % Organization
{San Francisco, California} % Location
{Jun. 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Won \textbf{1st place} for the Clover challenge and won \textbf{3rd place} at the Global AI Hackathon}
\item {Developed middleware for Clover Payment Devices to prevent fraudulent activity via Facial Recognition}
\item {Designed a facial recognition program using TensorFlow to detect if a user is the person authorized to use the credit card}
\item {Deployed a server using Google Cloud Platform to handle the requests for authenticating a user from the Clover device}
\item {Integrated Clover's Android SDK to create a custom tender option that takes a picture of the person checking out to identify whether or not the person is fraudulent}
\end{cvitems}
}

\begin{comment}
\cventry
{Team Lead} % Job title
{Machine Learning API} % Organization
{San Francisco, California} % Location
{Jun. 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed an API for commonly used machine learning models to support Hackathon team's artificial intelligence applications}
\item {Deployed an API via Google Cloud to interface Clover payment devices and Chui's API}
\end{cvitems}
}
\end{comment}

\begin{comment}
\cventry
{Solo} % Job title
{Text File Compression} % Organization
{San Luis Obispo, California} % Location
{Oct. 2016 - Nov. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented Huffman Coding to compress text files in Java and C}
\item {Designed complimentary encoding program to compress files into characters to serve an educational purpose for those learning how compression works}
\end{cvitems}
}
\end{comment}

\begin{comment}
\cventry
{Software Lead} % Job title
{Flash Card iOS Study Tool} % Organization
{San Luis Obispo, California} % Location
{Oct. 2015 - Dec. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed an iOS application to help groups of students study together with a flashcard like application} \item {Utilized device's accelerometer to navigate through application's storyboard}
\item {Used Swift and MongoDB to allow local and remote storage for the data necessary for the application}
\end{cvitems}
}
\end{comment}
\end{cventries}
